Corpus Stats

### 2019-03-22 notebooks/corpus_stats_and_plots.Rmd
put in plots, i will tinker with them over the next bit

Similar to the R stuff.
Now, we should combine these plots.
```{r}
combo_df <- r_c_df
combo_df$loc_c <- c_c_df$loc_c
combo_df$loc_r <- sapply(combo_df$loc_r, function(x) if (x == 0) x else log10(x))
combo_df$loc_c <- sapply(combo_df$loc_c, function(x) if (x == 0) x else log10(x))

# sort
combo_df <- combo_df[order(combo_df$loc_r), ]

# TODO: not staying sorted, probably id.vars
zzz <- melt(combo_df, id.vars="package_name", variable.name = "language")

plot_both <- ggplot( data=zzz, aes(package_name, value, group=1))
plot_both <- plot_both + geom_line(aes(colour = language)) + geom_point(aes(colour = language))
plot_both <- plot_both + labs(
  title = "Analysis of R Corpus (R and C)",
  x = "Corpus of Analyzed Packages", 
  y = "Lines of Code in Package (Log10-scaled)"
)

plot_both <- plot_both + theme(axis.text.x = element_blank())

# plot it
plot_both
```

>>>>

Similar to the R stuff.
Now, we should combine these plots.
Messy graphs, beware!
```{r}
combo_df <- r_c_df
combo_df$loc_c <- c_c_df$loc_c
combo_df$loc_r <- sapply(combo_df$loc_r, function(x) if (x == 0) x else log10(x))
combo_df$loc_c <- - sapply(combo_df$loc_c, function(x) if (x == 0) x else log10(x))

# sort
combo_df <- combo_df[order(combo_df$loc_r), ]
# this makes sure the package_names are in the right order, ggplot2 plots according to factors
# and levels
combo_df$package_name <- factor(combo_df$package_name, levels=combo_df$package_name)

# TODO: not staying sorted, probably id.vars
zzz <- melt(combo_df, id.vars="package_name", variable.name = "language")
# zzz_c <- melt(combo_df_c, id.vars="package_name", variable.name = "language")

plot_both <- ggplot( data=zzz, aes(package_name, value, group=1))
plot_both <- plot_both + geom_line(aes(colour = language), size=0.001) # +  geom_point(aes(colour = language))
plot_both <- plot_both + labs(
  title = "Analysis of R Corpus (R and C)",
  y = "Lines of Code in Package (Log10-scaled)"
)

plot_both <- plot_both + theme(axis.text.x = element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank()) + scale_y_continuous(name="Lines of Code in Package") # , breaks = c(-4, -3, -2, -1, 0, 1, 2, 3, 4), labels = function(x) abs(x^10)

# plot it
plot_both

ggsave("../paper/plots/linesofrandccode.pdf", plot_both)

Changing gears, lets get the number of recorded events by package.
Final numbers will become available as the trace completes.
```{r}

records_by_fun <- unlist(readRDS("../data/total_list_of_records_by_pkg.RDS"))
records_by_fun_df <- data.frame(pname=names(records_by_fun), records=unname(records_by_fun))
# records_by_fun_df <- records_by_fun_df[order(records_by_fun_df$records), ]
# records_by_fun_df$pname <- factor(records_by_fun_df$pname, levels=records_by_fun_df$pname)

plot_records <- ggplot(data=records_by_fun_df, aes(x=pname, y=records, group=1)) +
                geom_line() + 
                labs( title = "Numbers of Recorded Signatures",
                      y = "Recorded Traces in a Package (Thousands)") +
                theme(axis.text.x = element_blank(), axis.title.x=element_blank(),
                      axis.ticks.x=element_blank())

# plot
plot_records

# generate file
ggsave("../paper/plots/recordsbypkg.pdf", plot_records)
```
